Emulating Comparative Oncology Trials with Real-world Evidence Studies (ENCORE): Process Development and Methodological Considerations for Oncology Real-World Data

### 2025-10-22 manuscript/manuscript.qmd
updated word count
implemented changes that were introduced in the final FDA cleared version

**Authors**: Janick Weberpals^1^, Sebastian Schneeweiss^1^, Kenneth L. Kehl^2^, Donna R. Rivera^3^, Pallavi Mishra-Kalyani^3^, Catherine C. Lerro^3^, Erin Larkins^4^, Sonia Singh^4\*^, Preeti Narayan^4^, Richard Curley^4^, Georg Hahn^1^, Priyanka Anand^1^, Yanina Natanzon^5^, Andrew J. Belli^6^, Ching-Kun Wang^6^, Jenna Collins^7^**,** Jonathan Kish^7^**,** Janet Espirito^8^, Nicholas J Robert^8^, Robert J. Glynn^1^, Shirley V. Wang^1^

@@

[**Abstract word count:**]{.underline} 228 words / 250 words

@@

[**Funding Statement:**]{.underline} This project was supported by an FDA BAA contract with contract number 75F40122C00181.

>>>>

**Authors**: Janick Weberpals^1^, Sebastian Schneeweiss^1^, Kenneth L. Kehl^2^, Donna R. Rivera^3\*^, Pallavi Mishra-Kalyani^3^, Catherine C. Lerro^3\*^, Erin Larkins^4^, Preeti Narayan^4^, Richard Curley^3^, Georg Hahn^1^, Priyanka Anand^1^, Yanina Natanzon^5^, Andrew J. Belli^6^, Ching-Kun Wang^6^, Jenna Collins^7^**,** Jonathan Kish^7^**,** Janet Espirito^8^, Nicholas J Robert^8^, Robert J. Glynn^1^, Shirley V. Wang^1^

@@

[**Abstract word count:**]{.underline} 224 words / 250 words

@@

[**FDA Disclaimer:**]{.underline}This article reflects the views of the authors and should not be construed to represent FDA’s views or policies.

[**Funding Statement:**]{.underline} This project was supported by the Oncology Center of Excellence, Food and Drug Administration (FDA) of the U.S. Department of Health and Human Services (HHS) as part of a contract \[75F40122C00181\]. The contents are those of the author(s) and do not necessarily represent the official views of, nor an endorsement by FDA/HHS, or the U.S. Government.
